Measuring Directionality in Double Beta Decay and Neutrino Interactions with Kiloton-Scale Scintillation Detectors

### 2013-07-18 Direction.tex
Add J.M. Conrad to acknowledgements. --Lindley
Add Andrey Figures and put them in a nice full page figure. --Lindley

\section{Energy Dependence and Detector Size}
\label{edep_size_sec}
include this?

The number of Cerenkov photons decreases disproportionally with decreasing electron energy. The number of PEs after the 34.0~ns time cut for 1~MeV electrons is 37 PE from scintillation and 13 PE from Cerenkov light. This illustrates that directionality reconstruction benefits from higher initial energies but even at 1~MeV there might be accessible directionality information.

An additional set of simulations of a 0.65~m diameter ($\approx$ 1~m$^3$) detector with otherwise default parameters was performed. In the smaller detector the chromatic dispersion is not as important and absorption in the scintillator bulk is reduced. The latter effect increases the absolute number of photoelectrons. The former effect, on one hand, reduces the separation in time between Cerenkov and Scintillation light. On the other hand, it reduces the broadening of both time distributions which helps more sophisticated vertex and track reconstruction with the help of fast photodetectors like for example the LAPPDs.

%tbd (calculate numbers): However, with the simplified effective vertex reconstruction and a time cut of 3.4~ns we get  PEs from scintillation and 87 PEs from Cerenkov. The time cut was adjusted such that the fraction of selected PEs from Cerenkov light matches the fraction in the large detector ($\approx$ 58\%). The QD spectrum discussed in section \ref{scintillator_emission_sec} (both shifted and unshifted) did not change the PE time distribution significantly. We also simulated the red-sensitive photocathode discussed in section \ref{detector_wavelength_response_sec} in the small detector. The amount of PE increases again significantly and with the 3.265~ns time cut the number of PE coming from Cerenkov light is 182 while the number of PE from scintillation light is 96.

In summary, the photodetector properties (TTS and QE) become more important relative to the scintillator emission and absorption spectra when the detector size is decreased from 6.5~m to 0.65~m.

%%idea: use (some) PMTs with high QE for high lambda (and/or low QE for normal lambda). 
%% add some more info why we are interested in a smaller detector
%% motivation: Daedalus/ISODAR (?), 0nuBB 
\section{Reconstruction}
\label{reconstruction_sec}
WCSimAnalysis is a Water Cherenkov reconstruction package developed by Andrew Blake for the Long Baseline Neutrino Experiment (LBNE collaboration). It provides a framework for generic event cleaning, track reconstruction, and particle id, and it comes equipped with variety of pre-built algorithms. A collaboration between Iowa State, the University of Chicago, and Argonne National Laboratory has continued adding to the code, developing new track-fitting techniques for Water Cherenkov detectors built around the unique capabilities of microchannel plate photodetectors (MCPs): timing resolutions below 100 picoseconds and imaging resolutions below a centimeter. In this paper, we use only the simple, low-level reconstruction tools native to the package, though in future works we hope to implement more sophisticated techniques.

@@

\begin{figure}
        \begin{center}
        \includegraphics[scale=0.20]{graphs/hDirX.pdf}
        \includegraphics[scale=0.20]{graphs/hDirY.pdf}
        \includegraphics[scale=0.20]{graphs/hDirZ.pdf}	
         \includegraphics[scale=0.20]{graphs/hVtxX.pdf}
        \includegraphics[scale=0.20]{graphs/hVtxY.pdf}
        \includegraphics[scale=0.20]{graphs/hVtxZ.pdf}	
        \caption[]{ We need a caption.}
        \end{center}
\end{figure}

@@

\section{Acknowledgements}
L. Winslow would like to thank for useful discussion on the topic. L. Winslow would also like to thank K. Arisaka for discussions on the possible reach of traditional PMTs and the characteristics of HPDs. A. Elagin, H.J. Frisch and M. Wetstein are supported by DOE XXXX. C. Aberle and L. Winslow are supported by funds from University of California Los Angeles.

>>>>

%%idea: use (some) PMTs with high QE for high lambda (and/or low QE for normal lambda). 
%% add some more info why we are interested in a smaller detector
%% motivation: Daedalus/ISODAR (?), 0nuBB 
\section{Reconstruction}
\label{reconstruction_sec}

\begin{figure*}[tbh]
        \begin{center}
        \subfigure{\includegraphics[scale=0.295]{graphs/hDirX_v1.pdf}}
        \subfigure{\includegraphics[scale=0.295]{graphs/hDirY_v1.pdf}}
        \subfigure{\includegraphics[scale=0.295]{graphs/hDirZ_v1.pdf}}
        \subfigure{\includegraphics[scale=0.295]{graphs/hVtxX_v1.pdf}}
        \subfigure{\includegraphics[scale=0.295]{graphs/hVtxY_v1.pdf}}
        \subfigure{\includegraphics[scale=0.295]{graphs/hVtxZ_v1.pdf}}
        \caption[]{We need a caption}
        \end{center}
\end{figure*}

WCSimAnalysis is a Water Cherenkov reconstruction package developed by Andrew Blake for the Long Baseline Neutrino Experiment (LBNE collaboration). It provides a framework for generic event cleaning, track reconstruction, and particle id, and it comes equipped with variety of pre-built algorithms. A collaboration between Iowa State, the University of Chicago, and Argonne National Laboratory has continued adding to the code, developing new track-fitting techniques for Water Cherenkov detectors built around the unique capabilities of microchannel plate photodetectors (MCPs): timing resolutions below 100 picoseconds and imaging resolutions below a centimeter. In this paper, we use only the simple, low-level reconstruction tools native to the package, though in future works we hope to implement more sophisticated techniques.

@@

@@

\section{Acknowledgements}
L. Winslow would like to thank J.M. Conrad for useful discussion on the topic. L. Winslow would also like to thank K. Arisaka for discussions on the possible reach of traditional PMTs and the characteristics of HPDs. A. Elagin, H.J. Frisch and M. Wetstein are supported by DOE XXXX. C. Aberle and L. Winslow are supported by funds from University of California Los Angeles.
